---
title: "GenerateReferenceData"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

The purpose of this document is to generate the necessary QC metrics for the reference datasets. Each
reference dataset is defined as a name and a path to celfiles.

# Reference Datasets
The default is to have two reference datasets, the nci60 and the MAQC data. However, you are welcome
to add other datasets in. To do this, create the necessary functions (patterned off of maqc.R or nci60.R) 
and add the calls below. By default, this creates a ```data/nci60``` and ```data/maqc``` directory that
stores the CEL files. The next step (below) will generate the QC metrics from this directory.
```{r create_reference_datasets}
create_nci60()
create_maqc()
```

# Reference QC Metrics
Given a series of references datasets under ```data```, generate QC metrics for each of these.

```{r generate_reference_QCMetrics}
data_files<-list.dirs(path="data")
data_files<-data_files[2:length(data_files)]
names(data_files)<-basename(data_files)

reference_QCMetrics<-generate_QCMetrics(data_files)

reference_QCMetrics[["nci60"]]$description<-""
reference_QCMetrics[["MAQC"]]$description<-"From the GEO website
https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE5350
Expression data from two distinct reference RNA samples (A and B) in four titration
pools were generated at multiple test sites using a variety of microarray-based and
alternative technology platforms. Sample A = Stratagene Universal Human Reference
RNA (UHRR, Catalog #740000), Sample B = Ambion Human Brain Reference RNA (HBRR,
Catalog #6050), Sample C = Samples A and B mixed at 75%:25% ratio (A:B); and
Sample D = Samples A and B mixed at 25%:75% ratio (A:B). In general, each microarray
platform was tested at three sites and each sample was tested in five replicates at
each test site. Samples (hybridizations) were named according to the following convention:
Platform_Testsite_SampleRelicate. For example, AFX_2_B1 represents the hybridization
(array) from platform AFX processed by test site 2 for the first replicate of sample B.
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3272078/"

saveRDS(reference_QCMetrics, file="reference_QCMetrics.rds")
```

# Conclusion
That's all there is to it. You should now have a ```reference_QCMetrics.rds``` file in the current directory
which can now be used as reference in this QC package.
